% Created 2021-01-20 Wed 15:21
% Intended LaTeX compiler: pdflatex
\documentclass[presentation]{beamer}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usetheme{default}
\author{Kyle Terrien}
\date{January 21, 2021}
\title{What is org-mode?}
\hypersetup{
 pdfauthor={Kyle Terrien},
 pdftitle={What is org-mode?},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.3)}, 
 pdflang={English}}
\begin{document}

\maketitle

\begin{frame}[label={sec:orgd5e9316}]{Problem space}
\begin{block}{You need a personal online notebook}
\begin{itemize}
\item You need to document things you learn and do.
\end{itemize}
\end{block}
\begin{block}{You need to write a lengthy document with complex formatting}
\begin{itemize}
\item Markdown doesn’t cut it.
\item Entry to \LaTeX{}-land is too expensive.
\item Word processor?  Surely you jest!
\end{itemize}
\end{block}
\begin{block}{You have a complex todo-list}
\begin{itemize}
\item Repeating events, deadlines, and dependencies
\item Each todo app has its own annoying quirks.
\end{itemize}
\end{block}
\end{frame}
\begin{frame}[label={sec:org1e6d28d}]{Solution: \href{https://orgmode.org/}{org-mode}, “Your life in plain text”}
\begin{itemize}
\item Outliner, markup language, and personal organizer
\item Exports into several output formats: HTML, PDF, ODT, man page, and
more.  The source format is plain text.
\item You’re looking at an example right now!
\end{itemize}
\end{frame}
\begin{frame}[label={sec:orgf9a596f},fragile]{But, it’s Emacs.  Eww!}
 \begin{block}{Yeah, it’s Emacs.  Get over it!}
\begin{itemize}
\item \texttt{C-h t} → Emacs tutorial
\end{itemize}
\end{block}
\begin{block}{Attached to vi?}
\begin{itemize}
\item evil-mode → vi keybindings, install through MELPA
\item \href{https://www.spacemacs.org/}{Spacemacs} → custom distribution with vi keybindings
\end{itemize}
\end{block}
\end{frame}
\begin{frame}[label={sec:org4315d56},fragile]{Basic org-mode}
 \begin{block}{Formatting}
\begin{itemize}
\item Typeset some things: Paragraph, list, image, table, code,
checkboxes
\end{itemize}
\end{block}
\begin{block}{Export to HTML, PDF, ODT}
\begin{itemize}
\item HTML: supports style sheets
\item PDF: \LaTeX{}, Beamer
\item ODT: for LibreOffice, supports templates
\end{itemize}
\end{block}
\begin{block}{Where is this going?}
\begin{itemize}
\item You can build a web site: OCLUG.org
\item You can create a slideshow: Beamer
\begin{itemize}
\item \texttt{M-x customize-group <RET> org-export}
\end{itemize}
\end{itemize}
\end{block}
\end{frame}
\begin{frame}[label={sec:orge195f58}]{Sneak peek}
\begin{itemize}
\item Org-agenda views
\end{itemize}
\end{frame}
\end{document}
